---
title: "Behind Biden's 2020 Win: Analyzing Key Influencers through Regression Models and Visualizations"
author: 
  - Pengyu Sui
  - Lin Dai
  - Xuecheng Gao
thanks: "Code and data are available at: https://github.com/simon0202sui/Political-support-in-the-US-2020.git"
date: today
date-format: long
abstract: "."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

```{r}
#| include: false
#| warning: false
#| message: false
#### Workspace setup ####
library(ggplot2)
library(arrow)
library(scales)
library(modelsummary)
library(tidyverse)
library(rstanarm)
library(knitr)
library(here)
library(marginaleffects)
# Read cleaned data
cleaned_data <- read_csv(file = "C:/Users/User/Desktop/Paper3/data_cleaned.csv")

# Read model
political_preferences <- readRDS(file = here::here("C:/Users/User/Desktop/Paper3/models/biden_support_model.rds"))
```

# Introduction




# Data {#sec-data}
```{r}
#| echo: false
#| message: false
#| label: fig-Age-gender
#| fig-cap: "Percentage of Biden Support by Age Group and Gender"

# Load the dataset
cleaned_data_survey <- read_csv("C:/Users/User/Desktop/Paper3/data_cleaned.csv")

# Filter the data for those who support Biden
biden_support <- cleaned_data_survey %>%
  filter(support_biden == "Yes")

# Calculate the counts of Biden supporters within each age group and gender
support_counts <- biden_support %>%
  group_by(age_group, gender) %>%
  summarise(count = n(), .groups = 'drop')

# Calculate the total number of Biden supporters by gender
total_supporters_by_gender <- support_counts %>%
  group_by(gender) %>%
  summarise(total_gender_supporters = sum(count), .groups = 'drop')

# Join the total supporters by gender back to the support counts to calculate percentages
percentage_both <- support_counts %>%
  left_join(total_supporters_by_gender, by = "gender") %>%
  mutate(percentage = (count / total_gender_supporters))

# Plot the horizontal bar chart for males and females
plot_gender <- ggplot(percentage_both, aes(x = age_group, y = percentage * 100, fill = gender)) +  # Multiply by 100 for percentage
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(percentage * 100), "%")),  # Multiply by 100 for percentage
            position = position_dodge(width = 0.9), vjust = -0.3, size = 3) +
  facet_wrap(~ gender) +  # Separate plots for each gender
  labs(x = "Age Group", y = "Percentage Support for Biden within Gender", fill = "Gender") +
  theme_minimal() +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

# Output the plot
plot_gender

```

```{r}
#| echo: false
#| message: false
#| label: fig-Race-gender
#| fig-cap: "Percentage of Biden Support by Race and Gender"

# Filter the data for those who support Biden
biden_support <- cleaned_data_survey %>%
  filter(support_biden == "Yes")

# Calculate the counts of Biden supporters within each race and gender
support_counts <- biden_support %>%
  group_by(race, gender) %>%
  summarise(count = n(), .groups = 'drop')

# Calculate the total number of Biden supporters by gender
total_supporters_by_gender <- support_counts %>%
  group_by(gender) %>%
  summarise(total_gender_supporters = sum(count), .groups = 'drop')

# Join the total supporters by gender back to the support counts to calculate percentages
percentage_race_gender <- support_counts %>%
  left_join(total_supporters_by_gender, by = "gender") %>%
  mutate(percentage = (count / total_gender_supporters))

# Plot the horizontal bar chart for race and gender
plot_race_gender <- ggplot(percentage_race_gender, aes(x = race, y = percentage * 100, fill = gender)) +  # Multiply by 100 for percentage
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(percentage * 100), "%")),  # Multiply by 100 for percentage
            position = position_dodge(width = 0.9), vjust = -0.3, size = 3) +
  facet_wrap(~ gender) +  # Separate plots for each gender
  labs(x = "Race", y = "Percentage Support for Biden within Gender", fill = "Gender") +
  theme_minimal() +
  coord_flip() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

# Output the plot
plot_race_gender

```

## Data Source



## Methodology

## Variables

## Measurement


# Model {#sec-model}

## Model set-up


## Model justification



# Results {#sec-results}


## Gender



## Race


## Age Group




`

# Discussion {#sec-discussion}

## Findings



## Women are more likely to vote for Biden



## Black, Asian, Hispanic, and Middle Eastern individuals are more likely to vote for Biden



## Non-gun owners are more likely to vote for Biden


## Future 


\newpage


\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check


## Diagnostics




\newpage


# References